Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-29 analysis/study2.qmd
updated study 2 html
added other primals to the correlates

data <- rbind(
  data, 
  pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE))

# data <- rbind(
#   data,
#   pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive"),
#   pool_coef(with = "PI_Changing", component="World Beliefs", name = "Changing"),
#   pool_coef(with = "PI_Enticing", component="World Beliefs", name = "Enticing"),
#   pool_coef(with = "PI_Good", component="World Beliefs", name = "Good"),
#   pool_coef(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical"),
#   pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe"),
#   pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable"),
# )
```

>>>>

# data <- rbind(
#   data, 
#   pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE))

data <- rbind(
  data,
  pool_coef(with = "PI_Alive", component="World Beliefs", name = "Alive", unequalrange=TRUE),
  pool_coef(with = "PI_Changing", component="World Beliefs", name = "Changing", unequalrange=TRUE),
  pool_coef(with = "PI_Enticing", component="World Beliefs", name = "Enticing", unequalrange=TRUE),
  pool_coef(with = "PI_Good", component="World Beliefs", name = "Good", unequalrange=TRUE),
  pool_coef(with = "PI_Hierarchical", component="World Beliefs", name = "Hierarchical", unequalrange=TRUE),
  pool_coef(with = "PI_Safe", component="World Beliefs", name = "Safe",unequalrange=TRUE),
  pool_coef(with = "PI_Understandable", component="World Beliefs", name = "Understandable",unequalrange=TRUE)
)
```
